\section{Introduction}

\subsection{Background}
In recent years, AI has been an growing topic. 
Many advancements have been made in several areas within AI including Computer Vision, Natural Language Processing, and other Machine Learning (ML) and Deep Learning (DL) projects \cite{AIAdv}.
With the release of LLM's such as ChatGPT and Dall-E, the public can now use these tools. 
However, the general public views AI as a negative advancement in technology. 
The main belief is that it reduces privacy, but can assist in other areas of life such as finding accurate information online
\cite{publicOpinion}.


\subsection{Project Description}
Our project was designed to show AI can be helpful tool.
Additionally, we are beginners in the realm of ML, so this project serves as a step towards real world problem solving.
The problem we sought to solve was Image Classification.
We employed several ML algorithms to perform Animal Classification for images.
Our goal was to learn how to do Image Classification using different methodologies to accurately predict whether an image contained one of the following animals: a cat, dog, or panda.

\subsection{Dataset Overview and Preparation}
The dataset used contained 3000 RGB images separated into 3 folders, 1 folder per animal \cite{Dataset}.
These images ranged varying sizes, ranging less than 100 pixels by 100 pixels to larger than 1000 pixels by 1000 pixels.
Each folder contained 1000 images of the depicted animal.
Not all images were representative of the subject described and were removed.
After cleaning the dataset, we had 2,952 images remaining.
Our criteria for removing images were as follows:

\begin{enumerate}
    \item Multiple interested animal species in the same image. eg. a cat and a dog within the same image.
    \item Too small of an image size: less than 100 pixels by 100 pixels.
    \item Subject of the image was not easily visible: caused by obscurities, filters, low resolution, etc.
    \item The image did not contain the subject animal.
\end{enumerate}

After cleaning the images, we further prepared the dataset to be entered into a readable format for the various models we selected. These included:
\begin{itemize}
    \item Resizing images to 500 pixels by 500 pixels or 224 pixels by 224 pixels
    \item Converting images to grayscale
    \item Converting images to arrays
    \item Creating new images by augmenting the given images using the following effects: rotation, zoom, horizontal flipping, vertical/horizonal shifting, shear transforming, and pixel filling.
\end{itemize}

With these changes in mind, the amount of data resulted in: 2,952 images and $(Length * Width * Color Mode) + 1$ Features. 
Thus for images in RGB sized 500 pixels by 500 pixels, we would have 750,001 features.
The reason for implementing these changes to the dataset was to improve performance of the models, as well as speed up the creation of the models.

\subsection{Outline}
The outline of this paper is as follows: First, we will discuss the research that contributed to our understanding and gave insights into beginning the project.
Second, we will describe the algorithms used as well as the techniques employed to achieve our goal of making image classifiers.
Afterwards, we will evaluate and compare the performance of our models.
Following the evaluations, we will summarize and draw conclusions from the results.
Lastly, we will discuss some future works that can be done to explore further into this topic.